---
title: "hto_dataset"
output: html_document
---

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '/home/rstudio/01_data/Faezeh/HTO_datasets_dl')
```


from this webpage this data was found: https://rnabioco.github.io/cellar/7_multimodal.html


```{r}
# Data URL
data_url <- "https://scrnaseq-workshop.s3-us-west-2.amazonaws.com"

# Function to import counts
import_counts <- function(file_name, file_url = data_url) {
  mtx <- file.path(file_url, file_name) %>%
    read_csv() %>%
    column_to_rownames("X1") %>%
    as.sparse()

  mtx
}
```



```{r}
library(Seurat)
library(tidyverse)
rna_mtx <- import_counts("CITEseq_cDNA.csv.gz")

# Import CITE-seq matrix
adt_mtx <- import_counts("CITEseq_ADT.csv.gz")

rownames(adt_mtx) <- str_c("adt-", rownames(adt_mtx))
# Import HTO matrix
hto_mtx <- import_counts("CITEseq_HTO.csv.gz")

hto_mtx[, 1:10]

```

```{r}

joint <- intersect(colnames(rna_mtx), colnames(hto_mtx))
rna_mtx <- rna_mtx[,joint]
hto_mtx <- as.matrix(hto_mtx[,joint])
test <- CreateSeuratObject(rna_mtx)
test[["HTO"]] <- CreateAssayObject(counts = hto_mtx)
test
```

#Demultiplexing hashed samples
```{r}
test <- test %>%
  NormalizeData(
    assay = "HTO",
    normalization.method = "CLR"
  )
```


```{r}
test <-  HTODemux(test, assay = "HTO", positive.quantile = 0.99)

```


```{r}
table(test$HTO_classification.global)
```

```{r}
# Setup Seurat object metadata
test$log10nUMI <- log10(test$nCount_RNA)
test$log10nGene <- log10(test$nFeature_RNA)
test$mitoRatio <- PercentageFeatureSet(object = test, pattern = "^MT-")
test$mitoRatio <- test@meta.data$mitoRatio / 100
test$pct_mt <- test@meta.data$mitoRatio * 100
metadata <- test@meta.data;metadata
```


#outlier histogram
```{r}
library(mixtools)
outlier_Histogram <- function(data, x, sigmas = 1:3, bins = 100,
                             show_zero = FALSE) {
  x_data <- data[, x]
  
  mixmdl = normalmixEM(x_data, k=2,maxit=10000,epsilon=1e-08, maxrestarts = 1000)
  mu <- mixmdl$mu[2]
  sigma <- mixmdl$sigma[2]
  # mu <- mean(x_data)
  # sigma <- sd(x_data)
  
  outs <- lapply(sigmas, function(n) {
    lower  <- mu - n * sigma
    higher <- mu + n * sigma
    n_low  <- sum(x_data < lower)
    n_high <- sum(x_data > higher)
    
    list(n = n, lower = lower, higher = higher,
         n_low = n_low, n_high = n_high)
  })
  sdnorm =
    function(x, mean=0, sd=1, lambda=1){lambda*dnorm(x, mean=mean, sd=sd)}
  
  gg <- ggplot(data, aes(x = !!ensym(x))) +
    geom_histogram(bins = 100, color = "black", fill = "gray",  
                   aes(y=..density.., fill=..count..)) +
    geom_vline(xintercept = mu, colour = "blue", linetype = "dashed") +
    annotate("text", x = mu, y = 0, label = "Mean", colour = "blue",
             angle = 90, hjust = -0.1, vjust = -0.5) +
    annotate("text", x = mu, y = Inf, label = round(mu, 3), colour = "blue",
             angle = 90, hjust = 1, vjust = -0.5)+
    stat_function(fun=sdnorm,args=list(mean=mixmdl$mu[1],sd=mixmdl$sigma[1], lambda=mixmdl$lambda[1]), color ="black")+
    stat_function(fun=sdnorm,args=list(mean=mixmdl$mu[2],sd=mixmdl$sigma[2], lambda=mixmdl$lambda[2]),color =  "black")+
    theme_minimal() +
    ylab("density")+
    theme(legend.position = "none")+
    ggtitle("")
  
  
  for (i in seq_along(outs)) {
    out <- outs[[i]]
    
    if (show_zero) {
      show_low  <- TRUE
      show_high <- TRUE
    } else {
      show_low  <- out$n_low > 0
      show_high <- out$n_high > 0
    }
    
    if (show_low) {
      gg <- gg +
        geom_vline(xintercept = out$lower, colour = "red", linetype = "dashed") +
        annotate("text", x = out$lower, y = 0,
                 label = paste0(out$n, " SD"), colour = "red",
                 angle = 90, hjust = -0.1, vjust = -0.5) +
        annotate("text", x = out$lower, y = Inf,
                 label = paste0(round(out$lower, 3),
                                " (", out$n_low, " lower)"),
                 colour = "red", angle = 90, hjust = 1, vjust = -0.5)
    }
    
    
    if (show_high) {
      gg <- gg +
        geom_vline(xintercept = out$higher, colour = "red", linetype = "dashed") +
        annotate("text", x = out$higher, y = 0,
                 label = paste0(out$n, "SD"), colour = "red",
                 angle = 90, hjust = -0.1, vjust = -0.5) +
        annotate("text", x = out$higher, y = Inf,
                 label = paste0(round(out$higher, 3),
                                " (", out$n_high, " higher)"),
                 colour = "red", angle = 90, hjust = 1, vjust = -0.5)
    }
  }
  
  
  return(gg)
}

#pdf(file='CiteFuse_method_hto_filt/umifilt_outliers_12hto_10xdataset.pdf', width = 15, height = 10)
outlier_Histogram(metadata, "log10nGene", sigmas = c(2,2.5, 3, 4))
#dev.off()
```
```{r}
statt <- summary(metadata$log10nUMI);statt
st_dev <- sd(metadata$log10nUMI);st_dev
lower_umi <- 3.478-(3*0.1953326);lower_umi
```

```{r}
statt <- summary(metadata$log10nGene);statt
st_dev <- sd(metadata$log10nGene);st_dev
lower_gene <- 3.093-(3*0.1412351);lower_gene
```



```{r}
outlierHistogram <- function(data, x, mads = 1:3, bins = 100,
                             show_zero = FALSE) {
  x_data <- data[, x]
  med    <- median(x_data)
  MAD    <- mad(x_data, center = med, na.rm = TRUE)
  
  outs <- lapply(mads, function(n) {
    lower  <- med - n * MAD
    higher <- med + n * MAD
    n_low  <- sum(x_data < lower)
    n_high <- sum(x_data > higher)

    list(n = n, lower = lower, higher = higher,
         n_low = n_low, n_high = n_high)
    
  })
    gg <- ggplot(data, aes(x = !!ensym(x))) +
      geom_histogram(bins = 100, color = "black", fill = "gray"
                     )+ #aes(y=..density.., fill=..count..) inside of geom_histogram
      geom_vline(xintercept = med, colour = "blue", linetype = "dashed") +
      annotate("text", x = med, y = 0, label = "Median", colour = "blue",
               angle = 90, hjust = -0.1, vjust = -0.5) +
      annotate("text", x = med, y = Inf, label = round(med, 3), colour = "blue",
               angle = 90, hjust = 1, vjust = -0.5) +
      theme_minimal() +
      ylab("frequency")+
      theme(legend.position = "none")+
      ggtitle("")
      # stat_function(fun=dnorm, color="red", args=list(mean=mean(x_data),
      #                                                     sd=sd(x_data)))
      
      
    cols <- scales::brewer_pal(palette = "Reds",
                               direction = -1)(length(mads) + 1)
    
    for (i in seq_along(outs)) {
      out <- outs[[i]]
      
      if (show_zero) {
        show_low  <- TRUE
        show_high <- TRUE
      } else {
        show_low  <- out$n_low > 0
        show_high <- out$n_high > 0
      }
      
      if (show_low) {
        gg <- gg +
          geom_vline(xintercept = out$lower, colour = cols[i], linetype = "dashed") +
          annotate("text", x = out$lower, y = 0,
                   label = paste0(out$n, " MADs"), colour = cols[i],
                   angle = 90, hjust = -0.1, vjust = -0.5) +
          annotate("text", x = out$lower, y = Inf,
                   label = paste0(round(out$lower, 3),
                                  " (", out$n_low, " lower)"),
                   colour = cols[i], angle = 90, hjust = 1, vjust = -0.5)
      }
      
      if (show_high) {
      gg <- gg +
        geom_vline(xintercept = out$higher, colour = "red", linetype = "dashed") +
        annotate("text", x = out$higher, y = 0,
                 label = paste0(out$n, "MADs"), colour = "red",
                 angle = 90, hjust = -0.1, vjust = -0.5) +
        annotate("text", x = out$higher, y = Inf,
                 label = paste0(round(out$higher, 3),
                                " (", out$n_high, " higher)"),
                 colour = "red", angle = 90, hjust = 1, vjust = -0.5)
    }
  }
    
    return(gg)
  }

outlierHistogram(metadata, "pct_mt", mads = 3:4)

```


# Remove low quality cells by gaussian mixture and 4MADs for mito percent. Here only pct_mt will be removed.
```{r}
test_pre <- subset(test, pct_mt < 16.274)
#test_pre <- subset(test, subset = nFeature_RNA > 10^2.669295 & nCount_RNA > 10^2.892002 & pct_mt < 16.274)
test_pre
```

```{r}

table(test_pre$HTO_classification.global)

```

```{r}
test_pre_neg<- subset(test_pre, idents = "Negative", invert = TRUE);test_pre_neg
table(test_pre_neg$HTO_classification.global)
```



#################################################################################################################################
```{r}
test
```


```{r}
hto_mtx <- as.matrix(hto_mtx)
```


```{r}
sce_cite <- preprocessing(list(RNA = rna_mtx,
                                  HTO = hto_mtx))
```

```{r}
sce_cite
```

```{r}

patterns <- c("^hg19-MT-", "^mm10-mt-","^MT-", "^mt-")
sce_cite<-addPerCellQC(sce_cite, subsets=list(Mito=grepl(paste(patterns, collapse="|"), rownames(sce_cite))))
sce_cite$log10nUMI <- log10(sce_cite$sum)
sce_cite$log10nGene <- log10(sce_cite$detected)
metadata <- sce_cite@colData
metadata <- as.data.frame(metadata)
```

```{r}
rownames(sce_cite)[unlist(lapply(rownames(sce_cite), function(x) grepl("^MT-", x)))]
```

```{r}
library(mixtools)
outlier_Histogram <- function(data, x, sigmas = 1:3, bins = 100,
                             show_zero = FALSE) {
  x_data <- data[, x]
  
  mixmdl = normalmixEM(x_data, k=2,maxit=10000,epsilon=1e-08, maxrestarts = 1000)
  mu <- mixmdl$mu[1]
  sigma <- mixmdl$sigma[1]
  
  outs <- lapply(sigmas, function(n) {
    lower  <- mu - n * sigma
    higher <- mu + n * sigma
    n_low  <- sum(x_data < lower)
    n_high <- sum(x_data > higher)
    
    list(n = n, lower = lower, higher = higher,
         n_low = n_low, n_high = n_high)
  })
  sdnorm =
    function(x, mean=0, sd=1, lambda=1){lambda*dnorm(x, mean=mean, sd=sd)}
  
  gg <- ggplot(data, aes(x = !!ensym(x))) +
    geom_histogram(bins = 100, color = "black", fill = "gray",  
                   aes(y=..density.., fill=..count..)) +
    geom_vline(xintercept = mu, colour = "blue", linetype = "dashed") +
    annotate("text", x = mu, y = 0, label = "Mean", colour = "blue",
             angle = 90, hjust = -0.1, vjust = -0.5) +
    annotate("text", x = mu, y = Inf, label = round(mu, 3), colour = "blue",
             angle = 90, hjust = 1, vjust = -0.5)+
    stat_function(fun=sdnorm,args=list(mean=mixmdl$mu[1],sd=mixmdl$sigma[1], lambda=mixmdl$lambda[1]), color ="black")+
    stat_function(fun=sdnorm,args=list(mean=mixmdl$mu[2],sd=mixmdl$sigma[2], lambda=mixmdl$lambda[2]),color =  "black")+
    theme_minimal() +
    ylab("density")+
    theme(legend.position = "none")+
    ggtitle("")
  
  
  for (i in seq_along(outs)) {
    out <- outs[[i]]
    
    if (show_zero) {
      show_low  <- TRUE
      show_high <- TRUE
    } else {
      show_low  <- out$n_low > 0
      show_high <- out$n_high > 0
    }
    
    if (show_low) {
      gg <- gg +
        geom_vline(xintercept = out$lower, colour = "red", linetype = "dashed") +
        annotate("text", x = out$lower, y = 0,
                 label = paste0(out$n, " SD"), colour = "red",
                 angle = 90, hjust = -0.1, vjust = -0.5) +
        annotate("text", x = out$lower, y = Inf,
                 label = paste0(round(out$lower, 3),
                                " (", out$n_low, " lower)"),
                 colour = "red", angle = 90, hjust = 1, vjust = -0.5)
    }
    
    
    if (show_high) {
      gg <- gg +
        geom_vline(xintercept = out$higher, colour = "red", linetype = "dashed") +
        annotate("text", x = out$higher, y = 0,
                 label = paste0(out$n, "SD"), colour = "red",
                 angle = 90, hjust = -0.1, vjust = -0.5) +
        annotate("text", x = out$higher, y = Inf,
                 label = paste0(round(out$higher, 3),
                                " (", out$n_high, " higher)"),
                 colour = "red", angle = 90, hjust = 1, vjust = -0.5)
    }
  }
  
  
  return(gg)
}
#setwd("/home/faezeh/Documents/")
#pdf(file='CiteFuse_method_hto_filt/genefilt_outliers_CITEseq_10xdataset.pdf', width = 15, height = 10)
outlier_Histogram(metadata, "log10nGene", sigmas = c(2,2.5, 3, 4))
#dev.off()
```

```{r}
sd(metadata$log10nGene)
```

```{r}
summary(metadata$log10nGene)
```

```{r}
sd(metadata$log10nUMI)
```

```{r}
summary(metadata$log10nUMI)
```

```{r}
outlierHistogram <- function(data, x, mads = 1:3, bins = 100,
                             show_zero = FALSE) {
  x_data <- data[, x]
  med    <- median(x_data)
  MAD    <- mad(x_data, center = med, na.rm = TRUE)
  
  outs <- lapply(mads, function(n) {
    lower  <- med - n * MAD
    higher <- med + n * MAD
    n_low  <- sum(x_data < lower)
    n_high <- sum(x_data > higher)

    list(n = n, lower = lower, higher = higher,
         n_low = n_low, n_high = n_high)
    
  })
    gg <- ggplot(data, aes(x = !!ensym(x))) +
      geom_histogram(bins = 100, color = "black", fill = "gray"
                     )+ #aes(y=..density.., fill=..count..) inside of geom_histogram
      geom_vline(xintercept = med, colour = "blue", linetype = "dashed") +
      annotate("text", x = med, y = 0, label = "Median", colour = "blue",
               angle = 90, hjust = -0.1, vjust = -0.5) +
      annotate("text", x = med, y = Inf, label = round(med, 3), colour = "blue",
               angle = 90, hjust = 1, vjust = -0.5) +
      theme_minimal() +
      ylab("frequency")+
      theme(legend.position = "none")+
      ggtitle("")
      # stat_function(fun=dnorm, color="red", args=list(mean=mean(x_data),
      #                                                     sd=sd(x_data)))
      
      
    cols <- scales::brewer_pal(palette = "Reds",
                               direction = -1)(length(mads) + 1)
    
    for (i in seq_along(outs)) {
      out <- outs[[i]]
      
      if (show_zero) {
        show_low  <- TRUE
        show_high <- TRUE
      } else {
        show_low  <- out$n_low > 0
        show_high <- out$n_high > 0
      }
      
      if (show_low) {
        gg <- gg +
          geom_vline(xintercept = out$lower, colour = cols[i], linetype = "dashed") +
          annotate("text", x = out$lower, y = 0,
                   label = paste0(out$n, " MADs"), colour = cols[i],
                   angle = 90, hjust = -0.1, vjust = -0.5) +
          annotate("text", x = out$lower, y = Inf,
                   label = paste0(round(out$lower, 3),
                                  " (", out$n_low, " lower)"),
                   colour = cols[i], angle = 90, hjust = 1, vjust = -0.5)
      }
      
      if (show_high) {
      gg <- gg +
        geom_vline(xintercept = out$higher, colour = "red", linetype = "dashed") +
        annotate("text", x = out$higher, y = 0,
                 label = paste0(out$n, "MADs"), colour = "red",
                 angle = 90, hjust = -0.1, vjust = -0.5) +
        annotate("text", x = out$higher, y = Inf,
                 label = paste0(round(out$higher, 3),
                                " (", out$n_high, " higher)"),
                 colour = "red", angle = 90, hjust = 1, vjust = -0.5)
    }
  }
    
    return(gg)
  }
  
setwd("/home/faezeh/Documents/")
pdf(file='CiteFuse_method_hto_filt/mitoMADsfilt_outliers_CITEseq_10xdataset.pdf', width = 15, height = 10)
outlierHistogram(metadata, "subsets_Mito_percent", mads = 1:4)
# p <- plot(fitd)
dev.off()
```

```{r}
sce_cite <- normaliseExprs(sce = sce_cite,
                              altExp_name = "HTO",
                              transform = "log")
```

```{r}
sce_cite <- scater::runTSNE(sce_cite,
                               altexp = "HTO",
                               name = "TSNE_HTO",
                               pca = TRUE)

```


```{r}
visualiseDim(sce_cite,
             dimNames = "TSNE_HTO") + labs(title = "tSNE (HTO)")

```

```{r}
sce_cite <- scater::runUMAP(sce_cite,
                               altexp = "HTO",
                               name = "UMAP_HTO")


visualiseDim(sce_cite,
             dimNames = "UMAP_HTO") + labs(title = "UMAP (HTO)")
```

```{r}
sce_cite <- crossSampleDoublets(sce_cite)
```


```{r}
table(sce_cite$doubletClassify_between_label)
```

```{r}
table(sce_cite$doubletClassify_between_class)

```


```{r}
visualiseDim(sce_cite,
             dimNames = "TSNE_HTO",
             colour_by = "doubletClassify_between_label")
```

#prepare datasets:
####################https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE152981##################


```{r}
library(readr)
hto.umis <- read_csv("GSM4631061_rna_PBMC.csv.gz")
hto.umis.mat <- as.matrix(hto.umis)
test <- hto.umis.mat
rownames(test) <- test[,1]
test <- test[,-c(1)]
mode(test) = "numeric"

saveRDS(test, "GSM4631061_rna_PBMC.rds")
```


```{r}
# Read in UMI count matrix for RNA
library(readr)
library(dplyr)
hto.umis <- readRDS("GSM4631061_rna_PBMC.rds")
hto.umis <- t(hto.umis)

# Read in HTO count matrix
hto.htos <- read_csv("GSM4631063_hto_PBMC.csv.gz")
#hto.htos <- t(hto.htos)
#colnames(hto.htos) <- hto.htos[1,]
hto.htos <- hto.htos[-c(1),]
rownames(hto.htos) <- hto.htos$X1
hto.htos <- t(hto.htos)

# Select cell barcodes detected in both RNA and HTO
cells.use <- intersect(colnames(hto.htos), colnames(hto.umis))

# Subset RNA and HTO counts by joint cell barcodes
hto.umis <- hto.umis[, cells.use]
hto.htos <- as.matrix(hto.htos[, cells.use])

library(Seurat)
# Setup Seurat object
pbmc.hashtag <- CreateSeuratObject(counts = hto.umis)

# Normalize RNA data with log normalization
pbmc.hashtag <- NormalizeData(pbmc.hashtag)
# Find and scale variable features
pbmc.hashtag <- FindVariableFeatures(pbmc.hashtag, selection.method = "mean.var.plot")
pbmc.hashtag <- ScaleData(pbmc.hashtag, features = VariableFeatures(pbmc.hashtag))

# Add HTO data as a new assay independent from RNA
pbmc.hashtag[["HTO"]] <- CreateAssayObject(counts = hto.htos)
# Normalize HTO data, here we use centered log-ratio (CLR) transformation
pbmc.hashtag <- NormalizeData(pbmc.hashtag, assay = "HTO", normalization.method = "CLR")
```



#############################https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE108313###########
```{r}

hto.umis <- read_tsv("GSM2895282_Hashtag-RNA.umi.txt.gz")
hto.umis <- as.data.frame(hto.umis) # convert to dataframe from tibble
rownames(hto.umis) <- hto.umis[,1] # first column as rownames
hto.umis$GENE <- NULL # Remove Gene column (is not a cell)
#hto.umis[1:5,1:5]
#saveRDS(hto.umis, "GSM2895282_Hashtag-RNA.umi.rds")

######################################################
hto.umis <- readRDS("GSM2895282_Hashtag-RNA.umi.rds")
hto.htos <- read_csv("GSM2895283_Hashtag-HTO-count.csv.gz")
hto.htos <- as.data.frame(hto.htos)
rownames(hto.htos) <- hto.htos$X1
hto.htos$X1 <- NULL
hto.htos <- slice(hto.htos, 1:(n()-3))

# Select cell barcodes detected in both RNA and HTO
cells.use <- intersect(colnames(hto.htos), colnames(hto.umis))


# Subset RNA and HTO counts by joint cell barcodes
hto.umis <- hto.umis[, cells.use]
hto.htos <- as.matrix(hto.htos[, cells.use])

library(Seurat)
# Setup Seurat object
pbmc.hashtag <- CreateSeuratObject(counts = hto.umis[, cells.use], min.features = 200)

# Normalize RNA data with log normalization
pbmc.hashtag <- NormalizeData(pbmc.hashtag)
# Find and scale variable features
pbmc.hashtag <- FindVariableFeatures(pbmc.hashtag, selection.method = "mean.var.plot")
pbmc.hashtag <- ScaleData(pbmc.hashtag, features = VariableFeatures(pbmc.hashtag))

# Add HTO data as a new assay independent from RNA

pbmc.hashtag[["HTO"]] <- CreateAssayObject(counts = hto.htos[1:8,colnames(pbmc.hashtag)])
# Normalize HTO data, here we use centered log-ratio (CLR) transformation
pbmc.hashtag <- NormalizeData(pbmc.hashtag, assay = "HTO", normalization.method = "CLR")
```

###########################################https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE156718###########################
```{r}
umi_data_dir <- "GSE156718_GEX"
umi.mtx <- Read10X(umi_data_dir)

hto_data_dir <- "GSE156718_HTO"
hto.mtx <- Read10X(hto_data_dir, gene.column = 1)
hto.mtx <- as.data.frame(hto.mtx)
hto.mtx <- slice(hto.mtx, 1:(n()-1))

mus.obj <- CreateSeuratObject(counts = umi.mtx)
mus.obj<- NormalizeData(mus.obj)
mus.obj <- FindVariableFeatures(mus.obj, selection.method = "mean.var.plot")
mus.obj <- ScaleData(mus.obj, features = VariableFeatures(mus.obj))

mus.obj[['HTO']] <- CreateAssayObject(counts = hto.mtx)
mus.obj <- NormalizeData(mus.obj, assay = "HTO", normalization.method = "CLR")

```

##################################https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE126310
```{r}
hto.umis <- read_delim("GSM3596095_ctrl-cDNA.txt.gz", delim = " ")
hto.umis <- as.data.frame(hto.umis)
rownames(hto.umis) <- hto.umis[,1] 
####################################
hto.htos <- read_csv("GSM3596097_ctrl-HTO-count.csv.gz")
hto.htos <- as.data.frame(hto.htos)
rownames(hto.htos) <- hto.htos$X1
hto.htos$X1 <- NULL
hto.htos <- slice(hto.htos, 1:(n()-3))

cells.use <- intersect(colnames(hto.htos), colnames(hto.umis))
hto.umis <- hto.umis[, cells.use]
hto.umis <- na.omit(hto.umis)
hto.htos <- as.matrix(hto.htos[, cells.use])

library(Seurat)
# Setup Seurat object
pbmc.hashtag <- CreateSeuratObject(counts = hto.umis)



# Normalize RNA data with log normalization
pbmc.hashtag <- NormalizeData(pbmc.hashtag)
# Find and scale variable features
pbmc.hashtag <- FindVariableFeatures(pbmc.hashtag, selection.method = "mean.var.plot")
pbmc.hashtag <- ScaleData(pbmc.hashtag, features = VariableFeatures(pbmc.hashtag))

# Add HTO data as a new assay independent from RNA
pbmc.hashtag[["HTO"]] <- CreateAssayObject(counts = hto.htos)
# Normalize HTO data, here we use centered log-ratio (CLR) transformation
pbmc.hashtag <- NormalizeData(pbmc.hashtag, assay = "HTO", normalization.method = "CLR")


#find NA 
which(is.na(pbmc.hashtag$nCount_RNA))
toRemove <- c("AAACCTGAGACAAAGG")

## filter them out:
pbmc.hashtag <- pbmc.hashtag[,!colnames(pbmc.hashtag) %in% toRemove]
```
##########################https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE108313 (mixcelllines)
```{r}
hto.umis <- read_tsv("GSM3501446_MixCellLines-RNA.umi.txt.gz")
hto.umis <- as.data.frame(hto.umis) # convert to dataframe from tibble
rownames(hto.umis) <- hto.umis[,1] # first column as rownames


hto.htos <- read_csv("GSM3501447_MixCellLines-HTO-counts.csv.gz")
rownames(hto.htos) <- hto.htos$X1
hto.htos$X1 <- NULL
x <- t(hto.htos)
x <- as.data.frame(x)
hto.htos <- slice(x, 1:(n() - 4))

# Select cell barcodes detected in both RNA and HTO
cells.use <- intersect(colnames(hto.htos), colnames(hto.umis))


# Subset RNA and HTO counts by joint cell barcodes
hto.umis <- hto.umis[, cells.use]
hto.htos <- as.matrix(hto.htos[, cells.use])

library(Seurat)
# Setup Seurat object
pbmc.hashtag <- CreateSeuratObject(counts = hto.umis[, cells.use], min.features = 300)

# Normalize RNA data with log normalization
pbmc.hashtag <- NormalizeData(pbmc.hashtag)
# Find and scale variable features
pbmc.hashtag <- FindVariableFeatures(pbmc.hashtag, selection.method = "mean.var.plot")
pbmc.hashtag <- ScaleData(pbmc.hashtag, features = VariableFeatures(pbmc.hashtag))

# Add HTO data as a new assay independent from RNA

pbmc.hashtag[["HTO"]] <- CreateAssayObject(counts = hto.htos[1:8,colnames(pbmc.hashtag)])
# Normalize HTO data, here we use centered log-ratio (CLR) transformation
pbmc.hashtag <- NormalizeData(pbmc.hashtag, assay = "HTO", normalization.method = "CLR")
```

https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE128879
```{r}
hto.umis <- read_tsv("/home/rstudio/01_data/Faezeh/HTO_datasets_dl/GSM3687893_Morphine_RNA_count.txt.gz")
hto.umis <- as.data.frame(hto.umis)
rownames(hto.umis) <- hto.umis[,1]
hto.umis$AACTTTCTCCCTTGCA <- NULL

hto.htos <- read_csv("/home/rstudio/01_data/Faezeh/HTO_datasets_dl/GSM3687894_Morphine_HTO_count.csv.gz")
rownames(hto.htos) <- hto.htos$X1
#hto.htos$X1 <- NULL
hto.htos <- as.data.frame(hto.htos)
hto.htos$X1 <- NULL

cells.use <- intersect(colnames(hto.htos), colnames(hto.umis))

# Subset RNA and HTO counts by joint cell barcodes
hto.umis <- hto.umis[, cells.use]
hto.htos <- as.matrix(hto.htos[, cells.use])

library(Seurat)
# Setup Seurat object

pbmc.hashtag <- CreateSeuratObject(counts = hto.umis[, cells.use])

# Normalize RNA data with log normalization
pbmc.hashtag <- NormalizeData(pbmc.hashtag)
# Find and scale variable features
pbmc.hashtag <- FindVariableFeatures(pbmc.hashtag, selection.method = "mean.var.plot")


pbmc.hashtag <- ScaleData(pbmc.hashtag, features = VariableFeatures(pbmc.hashtag))

# Add HTO data as a new assay independent from RNA

pbmc.hashtag[["HTO"]] <- CreateAssayObject(counts = hto.htos)
# Normalize HTO data, here we use centered log-ratio (CLR) transformation
pbmc.hashtag <- NormalizeData(pbmc.hashtag, assay = "HTO", normalization.method = "CLR")
```




https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE164378 CITE
```{r}
umi_data_dir <- "/home/rstudio/01_data/Faezeh/HTO_datasets_dl/GSE164378_CITE_RNA/"
umi.mtx <- Read10X(umi_data_dir)

hto_data_dir <- "/home/rstudio/01_data/Faezeh/HTO_datasets_dl/GSE164378_CITE_HTO/"
hto.mtx <- Read10X(hto_data_dir, gene.column = 1)
hto.mtx <- as.data.frame(hto.mtx)
hto.mtx <- slice(hto.mtx, 1:(n() - 12))
hto.mtx <- hto.mtx[, colSums(hto.mtx != 0) > 0]

cells.use <- intersect(colnames(hto.mtx), colnames(umi.mtx))
umi.mtx <- umi.mtx[, cells.use]
hto.mtx <- as.matrix(hto.mtx[, cells.use])

hum.obj <- CreateSeuratObject(counts = umi.mtx[, cells.use], min.features = 300)
hum.obj <- NormalizeData(hum.obj)
hum.obj <- FindVariableFeatures(hum.obj, selection.method = "mean.var.plot")
hum.obj <- ScaleData(hum.obj, features = VariableFeatures(hum.obj))

hum.obj[['HTO']] <- CreateAssayObject(counts = hto.mtx[1:12,colnames(hum.obj)])
hum.obj <- NormalizeData(hum.obj, assay = "HTO", normalization.method = "CLR")
```


https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE164378 ECCITE
```{r}
umi_data_dir <- "/home/rstudio/01_data/Faezeh/HTO_datasets_dl/GSE164378_ECCITE_RNA/"
umi.mtx <- Read10X(umi_data_dir)

hto_data_dir <- "/home/rstudio/01_data/Faezeh/HTO_datasets_dl/GSE164378_ECCITE_HTO/"
hto.mtx <- Read10X(hto_data_dir)
hto.mtx <- as.data.frame(hto.mtx)
hto.mtx <- slice(hto.mtx, 1:(n() - 12))
hto.mtx <- hto.mtx[, colSums(hto.mtx != 0) > 0]

cells.use <- intersect(colnames(hto.mtx), colnames(umi.mtx))
umi.mtx <- umi.mtx[, cells.use]
hto.mtx <- as.matrix(hto.mtx[, cells.use])

hum.obj <- CreateSeuratObject(counts = umi.mtx[, cells.use], min.features = 200)
hum.obj <- NormalizeData(hum.obj)
hum.obj <- FindVariableFeatures(hum.obj, selection.method = "mean.var.plot")
hum.obj <- ScaleData(hum.obj, features = VariableFeatures(hum.obj))

hum.obj[['HTO']] <- CreateAssayObject(counts = hto.mtx[1:12,colnames(hum.obj)])
hum.obj <- NormalizeData(hum.obj, assay = "HTO", normalization.method = "CLR")
```



#HTODemux
```{r}
#pbmc.hashtag <- mus.obj
pbmc.hashtag <- hum.obj
pbmc.hashtag <- HTODemux(pbmc.hashtag, assay = "HTO", positive.quantile = 0.99)
```

```{r}
table(pbmc.hashtag$HTO_classification.global)
```


#remove low quality cells:

```{r}
# Setup Seurat object metadata

pbmc.hashtag$log10nUMI <- log10(pbmc.hashtag$nCount_RNA)
pbmc.hashtag$log10nGene <- log10(pbmc.hashtag$nFeature_RNA)
pbmc.hashtag$mitoRatio <- PercentageFeatureSet(object = pbmc.hashtag, pattern = "^MT-") #hg19-MT-
pbmc.hashtag$mitoRatio <- pbmc.hashtag@meta.data$mitoRatio / 100
pbmc.hashtag$pct_mt <- pbmc.hashtag@meta.data$mitoRatio * 100
metadata <- pbmc.hashtag@meta.data
```

```{r}
head(as.data.frame(metadata))
```


#outlier histogram
```{r}
library(mixtools)
library(ggplot2)
outlier_Histogram <- function(data, x, sigmas = 1:3, bins = 100,
                             show_zero = FALSE) {
  x_data <- data[, x]
  
  mixmdl = normalmixEM(x_data, k=2,maxit=10000,epsilon=1e-08, maxrestarts = 1000)
  # mu <- mixmdl$mu[2] #mu <- mixmdl$mu[2]
  # sigma <- mixmdl$sigma[2] #sigma <- mixmdl$sigma[2]
  mu <- mean(x_data)
  sigma <- sd(x_data)
  
  outs <- lapply(sigmas, function(n) {
    lower  <- mu - n * sigma
    higher <- mu + n * sigma
    n_low  <- sum(x_data < lower)
    n_high <- sum(x_data > higher)
    
    list(n = n, lower = lower, higher = higher,
         n_low = n_low, n_high = n_high)
  })
  sdnorm =
    function(x, mean=0, sd=1, lambda=1){lambda*dnorm(x, mean=mean, sd=sd)}
  
  gg <- ggplot(data, aes(x = !!ensym(x))) +
    geom_histogram(bins = 100, color = "black", fill = "gray",  
                   aes(y=..density.., fill=..count..)) +
    geom_vline(xintercept = mu, colour = "blue", linetype = "dashed") +
    annotate("text", x = mu, y = 0, label = "Mean", colour = "blue",
             angle = 90, hjust = -0.1, vjust = -0.5) +
    annotate("text", x = mu, y = Inf, label = round(mu, 3), colour = "blue",
             angle = 90, hjust = 1, vjust = -0.5)+
    # stat_function(fun=sdnorm,args=list(mean=mixmdl$mu[1],sd=mixmdl$sigma[1], lambda=mixmdl$lambda[1]), color ="black")+
    # stat_function(fun=sdnorm,args=list(mean=mixmdl$mu[2],sd=mixmdl$sigma[2], lambda=mixmdl$lambda[2]),color =  "black")+
    theme_minimal() +
    ylab("density")+
    theme(legend.position = "none")+
    ggtitle("")
  
  
  for (i in seq_along(outs)) {
    out <- outs[[i]]
    
    if (show_zero) {
      show_low  <- TRUE
      show_high <- TRUE
    } else {
      show_low  <- out$n_low > 0
      show_high <- out$n_high > 0
    }
    
    if (show_low) {
      gg <- gg +
        geom_vline(xintercept = out$lower, colour = "red", linetype = "dashed") +
        annotate("text", x = out$lower, y = 0,
                 label = paste0(out$n, " SD"), colour = "red",
                 angle = 90, hjust = -0.1, vjust = -0.5) +
        annotate("text", x = out$lower, y = Inf,
                 label = paste0(round(out$lower, 3),
                                " (", out$n_low, " lower)"),
                 colour = "red", angle = 90, hjust = 1, vjust = -0.5)
    }
    
    
    if (show_high) {
      gg <- gg +
        geom_vline(xintercept = out$higher, colour = "red", linetype = "dashed") +
        annotate("text", x = out$higher, y = 0,
                 label = paste0(out$n, "SD"), colour = "red",
                 angle = 90, hjust = -0.1, vjust = -0.5) +
        annotate("text", x = out$higher, y = Inf,
                 label = paste0(round(out$higher, 3),
                                " (", out$n_high, " higher)"),
                 colour = "red", angle = 90, hjust = 1, vjust = -0.5)
    }
  }
  
  
  return(gg)
}

#pdf(file='CiteFuse_method_hto_filt/umifilt_outliers_12hto_10xdataset.pdf', width = 15, height = 10)
outlier_Histogram(metadata, "log10nGene", sigmas = c(2,2.5, 3, 4))
#dev.off()
```

```{r}
outlierHistogram <- function(data, x, mads = 1:3, bins = 100,
                             show_zero = FALSE) {
  x_data <- data[, x]
  med    <- median(x_data)
  MAD    <- mad(x_data, center = med, na.rm = TRUE)
  
  outs <- lapply(mads, function(n) {
    lower  <- med - n * MAD
    higher <- med + n * MAD
    n_low  <- sum(x_data < lower)
    n_high <- sum(x_data > higher)

    list(n = n, lower = lower, higher = higher,
         n_low = n_low, n_high = n_high)
    
  })
    gg <- ggplot(data, aes(x = !!ensym(x))) +
      geom_histogram(bins = 100, color = "black", fill = "gray"
                     )+ #aes(y=..density.., fill=..count..) inside of geom_histogram
      geom_vline(xintercept = med, colour = "blue", linetype = "dashed") +
      annotate("text", x = med, y = 0, label = "Median", colour = "blue",
               angle = 90, hjust = -0.1, vjust = -0.5) +
      annotate("text", x = med, y = Inf, label = round(med, 3), colour = "blue",
               angle = 90, hjust = 1, vjust = -0.5) +
      theme_minimal() +
      ylab("frequency")+
      theme(legend.position = "none")+
      ggtitle("")
      # stat_function(fun=dnorm, color="red", args=list(mean=mean(x_data),
      #                                                     sd=sd(x_data)))
      
      
    cols <- scales::brewer_pal(palette = "Reds",
                               direction = -1)(length(mads) + 1)
    
    for (i in seq_along(outs)) {
      out <- outs[[i]]
      
      if (show_zero) {
        show_low  <- TRUE
        show_high <- TRUE
      } else {
        show_low  <- out$n_low > 0
        show_high <- out$n_high > 0
      }
      
      if (show_low) {
        gg <- gg +
          geom_vline(xintercept = out$lower, colour = cols[i], linetype = "dashed") +
          annotate("text", x = out$lower, y = 0,
                   label = paste0(out$n, " MADs"), colour = cols[i],
                   angle = 90, hjust = -0.1, vjust = -0.5) +
          annotate("text", x = out$lower, y = Inf,
                   label = paste0(round(out$lower, 3),
                                  " (", out$n_low, " lower)"),
                   colour = cols[i], angle = 90, hjust = 1, vjust = -0.5)
      }
      
      if (show_high) {
      gg <- gg +
        geom_vline(xintercept = out$higher, colour = "red", linetype = "dashed") +
        annotate("text", x = out$higher, y = 0,
                 label = paste0(out$n, "MADs"), colour = "red",
                 angle = 90, hjust = -0.1, vjust = -0.5) +
        annotate("text", x = out$higher, y = Inf,
                 label = paste0(round(out$higher, 3),
                                " (", out$n_high, " higher)"),
                 colour = "red", angle = 90, hjust = 1, vjust = -0.5)
    }
  }
    
    return(gg)
  }

outlierHistogram(metadata, "pct_mt", mads = 2:4)

```
For data GSE152981 2.5 SD and 4MADs
For data GSE108313 only 4MADs for pct mito

```{r}
statt <- summary(metadata$log10nUMI);statt
st_dev <- sd(metadata$log10nUMI);st_dev
lower_umi <- 3.2897-(2.5*0.2122837);lower_umi
```

```{r}
statt <- summary(metadata$log10nGene);statt
st_dev <- sd(metadata$log10nGene);st_dev
lower_gene <- 2.850-(2.5*0.1499766);lower_gene
```
#### GSE152981 data
```{r}
pbmc.hashtag_pre <- subset(pbmc.hashtag, subset = nFeature_RNA > 10^2.475059 & nCount_RNA > 10^2.758991 & pct_mt < 9.094)
pbmc.hashtag_pre
```
#### GSE108313 data
```{r}
pbmc.hashtag_pre <- subset(pbmc.hashtag, subset = pct_mt < 5.409)
pbmc.hashtag_pre
```
#### GSE156718 data 

```{r}
pbmc.hashtag_pre <- subset(pbmc.hashtag, subset = nFeature_RNA > 10^3.044 & nCount_RNA > 10^3.300 & pct_mt < 8.523)
pbmc.hashtag_pre
```

#### GSE126310 ctrl data

```{r}
pbmc.hashtag_pre <- subset(pbmc.hashtag, subset = pct_mt < 16.261)
pbmc.hashtag_pre
```
#### mix cell lines
```{r}
pbmc.hashtag_pre <- subset(pbmc.hashtag, subset = pct_mt < 9.753)
pbmc.hashtag_pre
```

#### GSE128879

```{r}
#no prefiltering and negative, I use only pbmc.hashtag for label doublet and singlet
```

#### GSE164378_CITE
```{r}
pbmc.hashtag_pre <- subset(pbmc.hashtag, subset = nFeature_RNA > 10^2.834 & nCount_RNA > 10^3.25 & pct_mt < 11.500)
pbmc.hashtag_pre
```
#### GSE164378_CECITE
```{r}
pbmc.hashtag_pre <- subset(pbmc.hashtag, subset = nCount_RNA > 10^2.90 & pct_mt < 10.283)
pbmc.hashtag_pre
```


```{r}
table(pbmc.hashtag_pre$HTO_classification.global)
```


```{r}
pbmc.hashtag_pre_neg<- subset(pbmc.hashtag_pre, idents = "Negative", invert = TRUE);pbmc.hashtag_pre_neg
table(pbmc.hashtag_pre_neg$HTO_classification.global)
```


####################################################################
```{r}
saveRDS(pbmc.hashtag_pre_neg, "GSE152981_filt_label_cells.rds")
```

```{r}

saveRDS(pbmc.hashtag_pre_neg, "GSE108313_filt_label_cells.rds")
```


```{r}
saveRDS(pbmc.hashtag_pre_neg,"GSE156718_filt_label_cells.rds")
```

```{r}
saveRDS(pbmc.hashtag_pre_neg, "GSE126310_ctrl_filt_label_cells.rds")
```

```{r}
saveRDS(pbmc.hashtag_pre_neg,"GSE108313_mixcelllines_filt_label_cells.rds")
```

```{r}
saveRDS(test_pre_neg, "CITEseq_amazon_test_filt_label_cells.rds")
```

```{r}
saveRDS(hto12_pre_neg, "pbmc_hto12_10x_filt_label_cells.rds")
```

```{r}
saveRDS(pbmc.hashtag_pre_neg, "pbmc_hto8_10x_filt_label_cells.rds")
```

```{r}
saveRDS(pbmc.hashtag, "GSE128879_filt_label_cells.rds")
```

```{r}
saveRDS(pbmc.hashtag_pre_neg, "/home/rstudio/01_data/Faezeh/HTO_datasets_dl/GSE164378_CITE_filt_label_cells.rds")
```

```{r}
saveRDS(pbmc.hashtag_pre_neg, "/home/rstudio/01_data/Faezeh/HTO_datasets_dl/GSE164378_CECITE_filt_label_cells.rds")
```

```{r}
VlnPlot(test, "nCount_RNA")
```

```{r}
VlnPlot(pbmc.hashtag[,!is.na(pbmc.hashtag$nCount_RNA)], "nCount_RNA")
```
```{r}

```



